### 2023-11-22 chapters/background.tex
Update final paragraph

\paragraph{Self"=supervised learning}
\moretodo[inline]{Revise according to change of review papers.}
An alternative approach to representation learning is provided by self"=supervised learning \parencite{mikolov_efficient_2013,devlin_bert_2018,chen_simple_2020,schneider_wav2vec_2019} which is a form of unsupervised learning where the training objective is derived from the data itself. 
While it is fair to say that not all self"=supervised training objectives have as principled a motivation as the VAE ELBO does, they have shown impressive results within the fields of natural language processing \parencite{devlin_bert_2018,chen_simple_2020}, speech processing \parencite{schneider_wav2vec_2019}, and computer vision \parencite{chen_simple_2020}. 
We provide a review and comparison of self"=supervised methods and variational autoencoders for speech representation learning in \cref{chp:paper-brief}. 
In \cref{app:paper-review} we provide a comprehensive introduction to and review of self"=supervised learning in speech recognition. 
% For a deeper comparison of VAEs and self"=supervised methods for speech processing, we refer the reader to our paper \textcite{borgholt_brief_2022} included in \cref{chp:paper-brief}.

>>>>

\paragraph{Self"=supervised learning}
An alternative approach to representation learning is provided by self"=supervised learning \parencite{mikolov_efficient_2013,devlin_bert_2018,chen_simple_2020,schneider_wav2vec_2019} which is a form of unsupervised learning where the training objective is derived from the data itself. 
While it is fair to say that not all self"=supervised training objectives have as principled a motivation as the VAE ELBO does, they have shown impressive results within the fields of natural language processing \parencite{devlin_bert_2018,chen_simple_2020}, speech processing \parencite{schneider_wav2vec_2019}, and computer vision \parencite{chen_simple_2020}. 
We provide a review and comparison of self"=supervised methods and variational autoencoders for speech representation learning in \cref{chp:paper-brief}. 
In \cref{app:paper-review} we provide a comprehensive introduction to and review of self"=supervised learning in speech recognition.
